### 2015-11-05 CVPR16/Source/occlusion.tex
Reviewed occlusion.tex

Thus, we have modeled the transmission probability to effectively capture the effect of occlusion due to all traffic participants in a scene that lie along a particular ray. We reiterate that our reflection and transmission probabilities are continuous functions, which allows us to define continuous energy functions for association and 3D object localization, as described in the next section.

%\paragraph{Probabilistic occlusion levels}
%With the above modeling and using \eqref{eq:imgform},

%% We model the probability of a point $\mathbf{x}_j$ on a object $i$ getting successfully
%% observed in a camera image at point $\trackpj{t}$ is dependent up two factors,
%% (1) reflection and (2) transmission through intermediate space. The reflection
%% part ensures that there is an object to reflect a point at a certain region in
%% the 3D space while transmission part models occlusion.
%% \begin{align}
%%   P^{(ij)}_{\text{observation}} = P^{(ij)}_{\text{reflection}}P^{(j)}_{\text{transmission}}
%% \end{align}

%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \subsection{Reflection probability}
%% For Lambertian reflection we replace the surface normal with the
%% gradient of occupancy.
%% %
%% \begin{align}
%%   \Prefl = (\max \{0, \nabla \occf^\top
%%   \hat{\mathbf{r}_j}\})^2
%% \end{align}
%% %
%% where $\ray =
%% \frac{K^{-1}\trackpj{t}}{\|K^{-1}\trackpj{t}\|}$ is unit vector in the
%% direction of ray. The gradient in the direction opposite to ray yields -ve
%% probability which needs to be clipped off. Squaring the function keep it
%% smooth near zero.

%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \subsection{Transmission probability}
%% A model for transmission of light through a material of thickness $x$,
%% density $\rho$ and opacity $k_o$ is given by Beer-Lambert law 
%% %
%% \begin{align}
%%   I(x) = I_0e^{-k_o\rho x}
%% \end{align}
%% %

%% Since both opacity and density are represented by the occupancy function
%% $\occftot = \sum_i \occf$, and also the domain of our $\occftot$ is $[0, 1]$ instead of $[0,
%% \infty]$ as in case of $k_o$; we replace $e^{-k_o\rho}$ by the transparency
%% function $1 - \occftot$. So the transmission probability over a small distance
%% $d\lambda$ is given by
%% %
%% \begin{align}
%%   P_{\text{transmission}}(\lambda + d\lambda) =
%%   P_{\text{transmission}}(\lambda) (1-\occftot)^{d\lambda}
%% \end{align}
%% %

%% For a given 3D point $\mathbf{x}_j = \lambda \ray$, the probability that the
%% point $\trackpj{t}$ is reflected from a distance $\lambda$ is given by

%% \begin{align}
%%   %P^{(j)}_{\text{observation}}(\lambda) &= P_{\text{reflection}}
%%   \Ptrans &=
%%   \prod_{0}^{\lambda} (1 - \occft{\lambda \ray})^{d\lambda} %\\
%%   %= \max \{ 0, (\nabla f_{occ}&(\lambda \ray)^\top \ray) \}
%%   %\prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda}
%%   \label{eq:ptrans-integral}
%% \end{align}
%% where $\prod_{0}^{\lambda}$ represents the \emph{product integral} from $0$ to
%% $\lambda$.

%% In practice, the integral for transmission probability
%% \eqref{eq:ptrans-integral} is difficult to compute even numerically. So we
%% choose a product of sigmoid function that approximates the behaviour of
%% transmission probability,
%% %
%% \begin{align}
%% \label{eq:evalCumulativePtrans}
%%   \Ptrans &= \prod_i L_u(\trackp{t}; \muiu,\Sigmaiu)L_{\lambda}(\lambda; \mu^i_d)
%% \end{align}
%% %
%% where $L_u(.)$ is sigmoid in image domain with $\mu^i_u$ and $\Sigma^i_u$
%% representing the elliptical projection of $i^{th}$ TP.
%% $L_{\lambda}(.)$ is sigmoid in the depth domain with $\mu^i_d$ as the mean
%% depth of the $i^{th}$ TP.
%% %
%% \begin{align}
%%   L_u(\mathbf{u}; \muiu,\Sigmaiu) &= \frac{1}{
%%     1 + e^{-k_u(1 - (\mathbf{u} - \muiu)^\top\Sigmaiu(\mathbf{u} -
%%     \muiu))}
%%   }
%%   \\
%%   L_{\lambda}(\lambda; \mu^i_d) &= \frac{1}{
%%     1 + e^{-k_d(\lambda - \mu^i_d)}
%% }
%% \end{align}
%% %

%% \begin{comment}%% Comment
%%   A product integral is a simple integral in log domain
%%   \begin{align}
%%     \prod_{0}^{\lambda} (1 - f_{occ}(\lambda \ray))^{d\lambda} =
%%     e^{\int_{1}^{\lambda} \ln{(1 - f_{occ}(\lambda \ray))}{d\lambda}}
%%   \end{align}
%% \end{comment}%% Comment

% \paragraph{Notation}
% We summarize the notation used in the report for quick reference.
% \\
% 
% 
%   \begin{tabular}{|l|l|}
%     \hline
%     Symbol & Meaning \\
%     \hline
%     $\pos{i}{t}$ & Position of $i$th car at time $t$\\
%     $\ori{i}{t}$ & Orientation of $i$th car at time $t$\\
%      $\dimsn{i}$ & 3D bounding box of the car (dimensions)\\
%     $\state{i}{t}$ & State of car $=\{\pos{i}{t}, \ori{i}{t}, \dimsn{i}\}$\\
%     $\egop$ & Position of camera at time $t$\\
%     $\egoo$ & Orientation of camera at time $t$\\
%     $\relp{i}{t}$ & Relative car pose w.r.t. camera \\
%     $\tracklets$ & 3D points tracked on car $i$ in its own frame\\
%     $\trackp{t}$ & Projection of $\tracklets$ in camera\\
%     $\projectionOf{.}$ & Projection function for pose $\relp{i}{t}$\\
%     $\bb{i}$ & 2D bounding box of the car in image\\
%     \hline
%   \end{tabular}

>>>>

Thus, we have modeled the transmission probability to effectively capture the
effect of occlusion due to all traffic participants in a scene that lie along a
particular ray. We reiterate that our reflection and transmission probabilities
are continuous functions, which allows us to keep the problem formulation in
continuous domain allowing for easier optimization.
